Slavnov products and KP tau functions

### 2025-04-29 draft.tex
finish tau function section

Evidently being a determinant is not enough to guarantee that the
Slavnov product is a tau function.  In order to accomplish this
result, we need to specify the models. Following the original
work~\cite{Belliard:2019bfz}, we will only discuss the rational models
-- we will see that the calculations are massive even in this simples
case. The generalization for open boundary conditions and for
trigonometric models is immediate, see~\cite{Slavnov:2019aba}
for more details on the generalization.

@@

We will now consider some concrete models.
We start with an R-matrix of the form
\begin{equation}
  R(u,v) = \mathbb{1} + g(u,v) \mathcal{P}\; , \qquad
  g(u,v) = \frac{c}{u - v}
\end{equation}
where \(c\) is a constant. Moreover \(\mathbb{1}\) is the identity operator and
\(\mathcal{P}\) is the permutation operator.

In the models with rational R-matrix, the eigenvalues of the transfer matrix
have the form 
\begin{equation}
  \Lambda(z, \bm{v}) = g(z, \bm{v}) \mathcal{Y}(z; \bm{v})\; ,
\end{equation}
where the function \(\mathcal{Y}(z; \bm{v})\) is symmetric over the
Bethe roots \(\bm{v}\), and linearly depends on every
\(v_j\). Generically, it is written as
\begin{equation}
  \mathcal{Y}(z; \bm{v}) = \sum_{p=0}^n \alpha_p(z) \sigma_p^{(n)}(\bm{v})\; , 
\end{equation}
where \(\sigma_p^{(n)}(\bm{v})\) are elementary symmetric polynomials
in \(\bm{v}\) and where \(\alpha_p(z)\) are free functional
parameters. In fact, in the XXX discussed in~\cite{Belliard:2019bfz},
these functions all \(\alpha_p(z)\) are polynomials of degree \(2n\). 
The important point for us is that \(\alpha_p(z)\) is not
singular when we consider the limit \(z \to v_j \in \bm{v}\),
so does the function \(\mathcal{Y}(z; \bm{v})\).

Furthermore, we have
\begin{equation}
  g(z, \bm{v}) = \prod_{v_i\in \bm{v}} g(z; v_i)\; , 
\end{equation}
and that means that each Bethe root \( v_i \in \bm{v}\) of this expression
is a pole of \(g(z;\bm{v})\). Therefore, if \(\gamma_j\) is a contour
containing the point \(v_j\), we have 
\begin{equation}
  \frac{1}{2 \pi i}\oint_{\gamma_j} \mathrm{d}z g(z; \bm{v}) = \prod_{v_i \in \bm{v}\setminus \{u_j\}} g(z, v_i)\; .
\end{equation}

The coefficients \(L_{jk}\) are given by \todo{\tiny Check references
  1, 2 of the paper to see the trigonometric case.}
\begin{equation}
  L_{jk} = g(u_k, \bm{u}_k) \mathcal{Y}(u_k; \bm{u}_j)
\end{equation}
and from this expression one can calculate the matrix \(\bm{M}\).
Finally, the authors also show that if \(\det (\bm{M}) = 0 \) and
\(\mathrm{rank}(\bm{M}) = n\), then, the Slavnov products are given by
\begin{equation}
 \bm{\zeta}_\ell = \phi(\bm{v}) \tilde{\Delta}(\bm{u}_\ell)\hat{\Omega}_\ell\; ,
\end{equation}
where \(\phi(\bm{v})\) is a function of the Bethe roots, and also
\begin{equation}
  \tilde{\Delta}(\bm{u}_\ell) = \prod_{\substack{u_j, u_j \in \bm{u}_\ell \\ j>k}} \frac{c}{u_j - u_k}\; . 
\end{equation}
Therefore, we can absorb the product of the constant \(c\) into
a unique constant \(c_0\) so that 
\begin{equation}
  \frac{\tilde{\Delta}(\bm{u}_\ell)}{c_0} = \prod_{\substack{u_j, u_j \in \bm{u}_\ell \\ j>k}} \frac{1}{u_j - u_k}\; , 
\end{equation}
that is the inverse of the Vandermonde determinant
\(\Delta(\bm{u}_\ell) = \prod_{j>k}(u_j - u_k)\).
Finally, we have  that \(\hat{\Omega}_\ell\) are minors of the matrix \(\bm{\Omega}\) with the \(\ell\)-th
column excluded, that is 
\begin{equation}
 \hat{\Omega}_\ell = \det_{k\neq \ell} \Omega_{jk}\; ,
\end{equation}
where
\begin{equation}
  \Omega_{jk} = g(u_k, v_j) \mathcal{Y}(u_k; \{u_k, \bm{v}_j\})
  \qquad j= 1, \dots, n\; , \quad k =1, \dots, n+1
\end{equation}

All in all, we have an expression of the
form
\begin{equation}
  \bm{\tau}_\ell(\bm{u}_\ell; \bm{v}) \equiv \frac{1}{c_0}\frac{\bm{\zeta}_\ell}{\phi(\bm{v})}
  = \frac{\det_{k\neq \ell} \Omega_{jk}}{\Delta(\bm{u}_\ell)}
\end{equation}

Let us now simplify these thing a little bit. First of all, we need to
observe that we can define \(n\) functions \(\Omega_j(z)\) of the form 
\begin{equation}
\begin{split}
  \Omega_{j}(z; \bm{v}) & = g(z, v_j) \mathcal{Y}(z; \{z, \bm{v}_j\})\qquad j =1, \dots, n\\
   & = \frac{c}{z - v_j} \mathcal{Y}(z; \{z, \bm{v}_j\})\; .
\end{split}
\end{equation}
Moreover, we have the expansion 
\begin{equation}
  \mathcal{Y}(z; \{z,\bm{v}_j\}) = \sum_{p=0}^n \alpha_p(z) \sigma_p^{(n)}(\{z,\bm{v}_j\})\; , 
\end{equation}
and using that the elementary symmetric polynomials decompose as
\begin{equation}
  \sigma_p^{(n)}(\{z,\bm{v}_j\}) = \sigma_p^{(n-1)}(\bm{v}_j) + z \sigma_{p-1}^{(n-1)}(\bm{v}_j) \; , 
\end{equation}
Therefore,
\begin{equation}
  \label{eq:y-functions-alpha}
  \mathcal{Y}_j(z)  = 
\sum_{p=0}^{n} \alpha_p(z)
  \left(\sigma_p^{(n-1)}(\bm{v}_j) + z \sigma_{p-1}^{(n-1)}(\bm{v}_j) \right) 
\end{equation}
where we have denoted \( \mathcal{Y}(z; \{z,\bm{v}_j\}) \equiv \mathcal{Y}_j(z)\). 
Observe that what defines the functions \(\mathcal{Y}_j(z)\) is the absence of the
\(j\)-th Bethe root \(v_j\).

Using that the elementary symmetric polynomials also satisfy \(\sigma_n^{(n-1)}(\bm{v}_j)=0\)
and \(\sigma_{-1}^{(n)}(\bm{v}_j)= 0\), we can write
\begin{equation}
  \label{eq:y-functions}
  \mathcal{Y}_j(z)  = 
  \sum_{p=0}^{n-1} 
   \left(\alpha_p(z) + z \alpha_{p+1}(z) \right) \sigma_p^{(n-1)}(\bm{v}_j) 
\end{equation}

We finally have 
\begin{equation}
  \Omega_{j}(z; \bm{v}) = -\frac{c}{v_j - z} \mathcal{Y}_j(z) \; .
\end{equation}
where we have denoted \( \mathcal{Y}(z; \{z,\bm{v}_j\}) \equiv \mathcal{Y}_j(z)\).
It is also convenient to consider \(c=1\).

%Finally, let us now consider this function in the neighborhood of the Bether root \(v_j\). We find 
%\begin{equation}
%  \Omega_j(z; \bm{v}) \simeq \frac{c}{z - v_j}
%\mathcal{Y}(v_j; \bm{v})\qquad j =1, \dots, n\; .
%\end{equation}

@@

Therefore, we can write the matrix \(\bm{\Omega}\) as 
\begin{equation}
  \bm{\Omega} =
  \begin{pmatrix}
    \Omega_1(u_1) & \dots & \Omega_1(u_n) & \Omega_1(u_{n+1}) \\
    \Omega_2(u_1) & \dots & \Omega_2(u_n) & \Omega_2(u_{n+1}) \\
    \vdots & \vdots & \vdots & \vdots \\
    \Omega_n(u_1) & \dots & \Omega_n(u_n) & \Omega_n(u_{n+1})
  \end{pmatrix}
\end{equation}
and we also define the \(n\times n\) matrices \(\bm\Omega^{(\ell)}(\bm{u}_\ell; \bm{v})\),
\(\ell = 1, \dots, n+1\), removing the \(\ell\)-th column of
\(\bm{\Omega}\), that is
\begin{equation}
  \bm{\Omega}^{(\ell)} =
  \begin{pmatrix}
    \Omega_1(u_1) & \dots & \Omega_1(u_{\ell-1}) & \Omega_1(u_{\ell+1})&\dots & \Omega_1(u_{n+1}) \\
    \vdots & \dots & \vdots & \vdots & \dots & \vdots \\
    \Omega_n(u_1) & \dots & \Omega_n(u_{\ell-1}) & \Omega_n(u_{\ell+1})&\dots & \Omega_n(u_{n+1})\; .
  \end{pmatrix}
\end{equation}

Putting these facts together, we write the functions
\begin{equation}
\label{eq:slavnov-tau-functions}
  \bm{\tau}_\ell(\bm{u}_\ell; \bm{v}) = \frac{\det [\Omega_j((\bm{u}_\ell)_k)]|_{j,k=1}^n }{\Delta(\bm{u}_\ell)} 
\end{equation}
where \((\bm{u}_\ell)_k \) is the k-th component of the vector
\(\bm{u}_\ell\). These functions are tau functions of the KP
hierarchy.  We have also omitted the dependence on the Bethe roots
\(\bm{v}\). The most important aspect now is that the poles of this
tau function are exactly the Bethe roots of the integrable model.

It is well documented that the functions defined as
in~(\ref{eq:slavnov-tau-functions}) are tau functions of the
KP-hierachy, see~\cite{Araujo:2021ghu} and references therein, in
particular~\cite{Kharchev:1991cy}.

In fact, we can focus all our attention on a particular function. Therefore,
for a fixed \(\ell\), we define the vector \( \bm{z} \equiv \bm{u}_\ell\).
Consequently, 
\begin{equation}
\begin{split}
\label{eq:tau-function}
  \bm{\tau}(\bm{z}, \bm{v})
  & = \frac{1}{\Delta(\bm{z})} \det[\Omega_j(z_k) ]_{j,k=1}^n \\
  & = \frac{1}{\Delta(\bm{z})} \det\left[\frac{\mathcal{Y}_j(z_k)}{z_k - v_j} \right]_{j,k=1}^n  \; .
\end{split}
\end{equation}
All these tau functions have the form of an \emph{alternant
determinant}.  Henceforth, we will only refer to the matrix
\(\bm{\Omega}\) defined by the components
\begin{equation}
  \label{eq:omega-matrix}
  \Omega_{jk} = \frac{\mathcal{Y}_j(z_k)}{z_k - v_j}\; .
\end{equation}

\subsection{Pole structure}

We now want to analyse the pole structure of
\(\Delta(\bm{z})\tau(\bm{z}, \bm{v})\).  First of all, one should
observe that the Bethe roots \(\bm{v}\) appear as poles of the
coefficients \(\bm{z}\). Moreover, lets us consideer here that the
Bethe roots are not degenerate, that is, if \(j \neq k\), then \(v_j
\neq v_k\). In that case, the poles \(v_j\) are simple poles.

Let us now consider a particular coefficient \(\bm{z}\), say \(z_l\), and
make a Laplace expansion in the column \(l\), that is
\begin{equation}
\begin{split}
  \bm{\tau}(\bm{z}, \bm{v})
  & = \frac{1}{\Delta(\bm{z})} \det[\bm{\Omega}(\bm{z}) ] \\
  & = \frac{1}{\Delta(\bm{z})} \sum_{j=1}^n (-1)^{j + l} \frac{\mathcal{Y}_j(z_l)}{z_l - v_j  } 
  \det[\hat{\Omega}_{j, l}]\; ,
\end{split}
\end{equation}
where \(\hat{\Omega}_{j,l} \) is the \((j, l)\) minor of \(\bm{\Omega}\).

Now, we can extract the residue of the tau function for \(z_l\) at the point \(v_j\), that is
\begin{equation}
  \Res_{(z_l, v_j)}(\Delta(\bm{z})\tau(\bm{z}, \bm{v})) = (-1)^{j+l} \mathcal{Y}_j(v_j) \det[\hat{\Omega}_{j, l}]
\end{equation}

Let us now decompose the Vandermonde determinant as
\begin{equation}
  \Delta(\bm{z}) = \prod_{j>k}(z_j - z_k) = \Delta(\bm{z}_l) \prod_{r<l}(z_l - z_r) \prod_{s>l}(z_s - z_l)\; ,
\end{equation}
where \(\bm{z}_l = \bm{z}\setminus \{z_l\} = (z_1, \dots, z_{l-1}, z_{l+1}, \dots, z_n) \).
\todo[inline]{I wand to verify that this is correct}
We can define the function
\begin{equation}
  \Xi_l(z_l,\bm{z}_l) = \prod_{r<l}(z_l - z_r) \prod_{r>l}(z_r - z_l)\; , 
\end{equation}
then 
\begin{equation}
  \Delta(\bm{z}) = \Xi_l(z_l, \bm{z}_l) \Delta(\bm{z}_l) \; .
\end{equation}

Let us now write
\begin{equation}
  \bm{\tau}(\bm{z}, \bm{v})
   = \frac{1}{\Xi_l(z_l, \bm{z}_l)} \sum_{j=1}^n (-1)^{j + l} \frac{\mathcal{Y}_j(z_l)}{z_l - v_j} 
\left(\frac{1}{\Delta(\bm{z}_l)} \det[\hat{\Omega}_{j, l}]\right)\; .
\end{equation}

When we define the set of functions
\begin{equation}
  \begin{split}
  \hat{\bm{\Omega}}_{(j)}(z) & = \left(\Omega_1(z), \dots, \Omega_{j-1}(z), \Omega_{j+1}(z), \dots, \Omega_n(z) \right)\; ,
  \end{split}
\end{equation}
we can simplify the tau function expansion even further. Then
\begin{equation}
\begin{split}
  \bm{\tau}(\bm{z}, \bm{v})
  & = \frac{1}{\Xi_l(z_l, \bm{z}_l)} \sum_{j=1}^n (-1)^{j + l} \frac{\mathcal{Y}_j(z_l)}{z_l - v_j} 
    \left(\frac{1}{\Delta(\bm{z}_l)} \det[\hat{\bm{\Omega}}_{(j) r}(\bm{z}_{(l) s} ]_{r, s=1}^n\right)\\ 
  & = \frac{1}{\Xi_l(z_l, \bm{z}_l)} \sum_{j=1}^n (-1)^{j + l} \frac{\mathcal{Y}_j(z_l)}{z_l - v_j} 
    \tilde{\bm{\tau}}_j(\bm{z}_l, \bm{v})\; ,
\end{split}
\end{equation}
where 
\begin{equation}
  \label{eq:basis-tau}
    \tilde{\bm{\tau}}_j(\bm{z}_l, \bm{v}) = 
\frac{1}{\Delta(\bm{z}_l)} \det[\hat{\bm{\Omega}}_{(j)}(\bm{z}_{(l)} ]\; .
\end{equation}
The curious aspect of this expression is that it easy to see that each term  
\(\tilde{\bm{\tau}}_j(\bm{z}_l, \bm{v})\) is a tau function itself, and that
it acts as a basis for the Slavnov's product. 
Additionally, these basis tau functions \(\tilde{\tau}_j(\bm{z}_l,
\bm{v})\) are, by construction, completely independent of \(z_l\).

@@

>>>>

Evidently being a determinant is not enough to guarantee that the
Slavnov product is a tau function.  In order to accomplish this
result, we need to specify the models. Following the original
work~\cite{Belliard:2019bfz}, we will only discuss the rational models
-- we will see that the calculations are overwhelming even in this
simple case. The generalization for open boundary conditions and for
trigonometric models is immediate, see~\cite{Slavnov:2019aba} for more
details on the generalization.

@@

Let us startwith an R-matrix of the form
\begin{equation}
  R(u,v) = \mathbb{1} + g(u,v) \mathcal{P}\; , \qquad
  g(u,v) = \frac{c}{u - v}
\end{equation}
where \(c\) is a constant, the identity operator is denoted by
\(\mathbb{1}\) and \(\mathcal{P}\) is the permutation operator.

In the models with rational R-matrix, the eigenvalues of the transfer matrix
have the form 
\begin{equation}
  \Lambda(z, \bm{v}) = g(z, \bm{v}) \mathcal{Y}(z; \bm{v})\; ,
\end{equation}
where the function \(\mathcal{Y}(z; \bm{v})\) is symmetric over the
Bethe roots \(\bm{v}\), and linearly depends on every
\(v_j\).

Generically, it is written as
\begin{equation}
  \mathcal{Y}(z; \bm{v}) = \sum_{p=0}^n \alpha_p(z) \sigma_p^{(n)}(\bm{v})\; , 
\end{equation}
where \(\sigma_p^{(n)}(\bm{v})\) are elementary symmetric polynomials
in \(\bm{v}\) and where \(\alpha_p(z)\) are free functional
parameters. In fact, in the XXX discussed in~\cite{Belliard:2019bfz},
these functions all \(\alpha_p(z)\) are polynomials of degree \(2n\).
The important point for us is that the functions \(\alpha_p(z)\) are
not singular when we consider the limit \(z \to v_j \in \bm{v}\), and
that also means that \(\mathcal{Y}(z; \bm{v})\) is also regular in
this limit.

Let us also define the following product 
\begin{equation}
  g(z, \bm{v}) = \prod_{v_i\in \bm{v}} g(z; v_i)\; , 
\end{equation}
and that means that each Bethe root \( v_i \in \bm{v}\) 
is a pole of \(g(z;\bm{v})\). Therefore, if \(\Gamma\) is a contour
containing all the Bethe roots \(\{v_j\}_{j=1}^n\), we have 
\begin{equation}
  \frac{1}{2 \pi i}\oint_{\Gamma} \mathrm{d}z g(z; \bm{v}) = \sum_{j=1}^n  \prod_{v_i \in \bm{v}\setminus \{u_j\}} g(z, v_i)\; .
\end{equation}
Furthermore, the coefficients \(L_{jk}\) are given by
\begin{equation}
  L_{jk} = g(u_k, \bm{u}_k) \mathcal{Y}(u_k; \bm{u}_j)
\end{equation}
and from this expression one can calculate the matrix \(\bm{M}\).

It has also been shown~\cite{Belliard:2019bfz} that if \(\det
(\bm{M}) = 0 \) and \(\mathrm{rank}(\bm{M}) = n\), then, the Slavnov
products are given by
\begin{equation}
 \bm{\zeta}_\ell = \phi(\bm{v}) \tilde{\Delta}(\bm{u}_\ell)\hat{\Omega}_\ell\; ,
\end{equation}
where \(\phi(\bm{v})\) is a function of the Bethe roots and
\begin{equation}
  \tilde{\Delta}(\bm{u}_\ell) = \prod_{\substack{u_j, u_j \in \bm{u}_\ell \\ j>k}} \frac{c}{u_j - u_k}\quad \Rightarrow \quad
\frac{\tilde{\Delta}(\bm{u}_\ell)}{c_0} = \prod_{\substack{u_j, u_j \in \bm{u}_\ell \\ j>k}} \frac{1}{u_j - u_k}\; , 
\end{equation}
where we have absorbed the product of \(c\) into a new constant \(c_0\). 
All in all, \(\tilde{\Delta}(\bm{u}_\ell)/c_0\) is the inverse of the Vandermonde determinant
\(\Delta(\bm{u}_\ell) = \prod_{j>k}(u_j - u_k)\).

Additionally, the matrices \(\hat{\Omega}_\ell\) are minors of
\(\bm{\Omega}\) with the \(\ell\)-th column excluded, in other words,
\begin{equation}
 \hat{\Omega}_\ell = \det_{k\neq \ell} \Omega_{jk}\; ,
\end{equation}
where
\begin{equation}
  \Omega_{jk}(u_k; \bm{v}) = g(u_k, v_j) \mathcal{Y}(u_k; \{u_k, \bm{v}_j\})\; ,
  \quad j= 1, \dots, n\; , \quad k =1, \dots, n+1\; .
\end{equation}

All in all, we have an expression of the form
\begin{equation}
  \label{eq:slavnov-tau}
  \bm{\tau}_\ell(\bm{u}_\ell; \bm{v}) \equiv \frac{1}{c_0}\frac{\bm{\zeta}_\ell}{\phi(\bm{v})}
  = \frac{\hat{\Omega}_{\ell}}{\Delta(\bm{u}_\ell)} \; .
\end{equation}
This is the most important result for us, and our goal now is to show
that it is a tau-function of the KP-hierarchy.

@@

In order to proceed, let us simplify the notation and organize the
results we described before. First of all, we need to observe
that we can define \(n\) functions \(\Omega_j(z)\) of the form
\begin{equation}
\begin{split}
  \Omega_{j}(z; \bm{v}) & = g(z, v_j) \mathcal{Y}(z; \{z, \bm{v}_j\})\qquad j =1, \dots, n\\
   & = \frac{c}{z - v_j} \mathcal{Y}(z; \{z, \bm{v}_j\})\; .
\end{split}
\end{equation}
Moreover, we have the expansion 
\begin{equation}
  \mathcal{Y}(z; \{z,\bm{v}_j\}) = \sum_{p=0}^n \alpha_p(z) \sigma_p^{(n)}(\{z,\bm{v}_j\})\; , 
\end{equation}
and using that the elementary symmetric polynomials decompose as
\begin{equation}
  \sigma_p^{(n)}(\{z,\bm{v}_j\}) = \sigma_p^{(n-1)}(\bm{v}_j) + z \sigma_{p-1}^{(n-1)}(\bm{v}_j) \; . 
\end{equation}

Let us also denote the functions
\begin{equation}
  \label{eq:y-functions-alpha}
  \mathcal{Y}_j(z)  \equiv  \mathcal{Y}(z; \{z,\bm{v}_j\})  = 
\sum_{p=0}^{n} \alpha_p(z)
  \left(\sigma_p^{(n-1)}(\bm{v}_j) + z \sigma_{p-1}^{(n-1)}(\bm{v}_j) \right) \; .
\end{equation}
Observe that the defining property of these functions
\(\mathcal{Y}_j(z)\) is the absence of the \(j\)-th Bethe root
\(v_j\).
Using that the elementary symmetric polynomials also satisfy \(\sigma_n^{(n-1)}(\bm{v}_j)=0\)
and \(\sigma_{-1}^{(n)}(\bm{v}_j)= 0\), we can write
\begin{equation}
  \label{eq:y-functions}
  \mathcal{Y}_j(z)  = 
  \sum_{p=0}^{n-1} 
   \left(\alpha_p(z) + z \alpha_{p+1}(z) \right) \sigma_p^{(n-1)}(\bm{v}_j) \; .
\end{equation}

Putting all these facts together, we have the functions
\begin{equation}
  \Omega_{j}(z; \bm{v}) = \frac{c}{z - v_j} \mathcal{Y}_j(z) \; .
\end{equation}
It is also convenient to consider \(c=1\), consequently \(c_0=1\).

\subsection{Alternant expression for the Slavnov products}

The matrix \(\bm{\Omega}\) can be written as
\begin{equation}
  \bm{\Omega} =
  \begin{pmatrix}
    \Omega_1(u_1) & \dots & \Omega_1(u_n) & \Omega_1(u_{n+1}) \\
    \Omega_2(u_1) & \dots & \Omega_2(u_n) & \Omega_2(u_{n+1}) \\
    \vdots & \vdots & \vdots & \vdots \\
    \Omega_n(u_1) & \dots & \Omega_n(u_n) & \Omega_n(u_{n+1})\; .
  \end{pmatrix}
\end{equation}
From this expression, we can also define a set of \(n\) square matrices
\(\bm\Omega^{(\ell)}(\bm{u}_\ell; \bm{v})\),
\(\ell = 1, \dots, n+1\), removing the \(\ell\)-th column of
\(\bm{\Omega}\), that is
\begin{equation}
  \bm{\Omega}^{(\ell)} =
  \begin{pmatrix}
    \Omega_1(u_1) & \dots & \Omega_1(u_{\ell-1}) & \Omega_1(u_{\ell+1})&\dots & \Omega_1(u_{n+1}) \\
    \vdots & \dots & \vdots & \vdots & \dots & \vdots \\
    \Omega_n(u_1) & \dots & \Omega_n(u_{\ell-1}) & \Omega_n(u_{\ell+1})&\dots & \Omega_n(u_{n+1})
  \end{pmatrix}\; .
\end{equation}

Finaly, we can write~(\ref{eq:slavnov-tau}) as 
\begin{equation}
\label{eq:slavnov-tau-functions}
  \bm{\tau}_\ell(\bm{u}_\ell; \bm{v}) = \frac{\det [\Omega_j((\bm{u}_\ell)_k)]|_{j,k=1}^n }{\Delta(\bm{u}_\ell)} 
\end{equation}
where \((\bm{u}_\ell)_k \) is the \(k\)-th component of the vector
\(\bm{u}_\ell\).  Therefore, for a fixed \(\ell\), we define the
vector \( \bm{z} \equiv \bm{u}_\ell\).  Consequently,
\begin{equation}
\begin{split}
\label{eq:slav-tau-function}
  \bm{\tau}(\bm{z}, \bm{v})
  & = \frac{1}{\Delta(\bm{z})} \det[\Omega_j(z_k) ]_{j,k=1}^n \\
  & = \frac{1}{\Delta(\bm{z})} \det\left[\frac{\mathcal{Y}_j(z_k)}{z_k - v_j} \right]_{j,k=1}^n  \; .
\end{split}
\end{equation}
All these tau functions have the form of an \emph{alternant
determinant} devided by the Vandermonde determinant.

It is well documented that the functions defined as
in~(\ref{eq:slav-tau-function}) are tau functions of the
KP-hierachy, see~\cite{Araujo:2021ghu} and references therein, in
particular~\cite{Kharchev:1991cy}. Consequently, these functions are
tau functions.

Henceforth, we will only refer to the matrix
\(\bm{\Omega}\) defined by the components
\begin{equation}
  \label{eq:omega-matrix}
  \Omega_{jk} = \frac{\mathcal{Y}_j(z_k)}{z_k - v_j}\; .
\end{equation}

\subsection{Tau functions expansion of the Slavnov product}

We can immediately observe that the poles of the tau
function~(\ref{eq:slav-tau-function}) are exactly the Bethe roots of
the integrable model.  We now want to analyse this pole structure of
\(\Delta(\bm{z})\tau(\bm{z}, \bm{v})\).  Let us consider that the
Bethe roots are not degenerate, that is, if \(j \neq k\), then \(v_j
\neq v_k\). In that case, the poles \(v_j\) are simple poles.

Let us now consider a particular coefficient \(\bm{z}\), say \(z_l\), and
make a Laplace expansion in the column \(l\), that is
\begin{equation}
\label{eq:minor-expansion}
\begin{split}
  \bm{\tau}(\bm{z}, \bm{v})
  & = \frac{1}{\Delta(\bm{z})} \det[\bm{\Omega}(\bm{z}) ] \\
  & = \frac{1}{\Delta(\bm{z})} \sum_{j=1}^n (-1)^{j + l} \frac{\mathcal{Y}_j(z_l)}{z_l - v_j  } 
  \det[\hat{\Omega}_{j, l}]\; ,
\end{split}
\end{equation}
where \(\hat{\Omega}_{j,l} \) is the \((j, l)\) minor of
\(\bm{\Omega}\).  Now, we can extract the residue of the tau function
for \(z_l\) at the point \(v_j\), that is
\begin{equation}
  \Res_{(z_l, v_j)}(\Delta(\bm{z})\tau(\bm{z}, \bm{v})) = (-1)^{j+l} \mathcal{Y}_j(v_j) \det[\hat{\Omega}_{j, l}]
\end{equation}

\begin{subequations}
Let us now decompose the Vandermonde determinant as
\begin{equation}
  \Delta(\bm{z}) = \prod_{j>k}(z_j - z_k) = \Delta(\bm{z}_l) \prod_{r<l}(z_l - z_r) \prod_{s>l}(z_s - z_l)\; ,
\end{equation}
where \(\bm{z}_l = \bm{z}\setminus \{z_l\} = (z_1, \dots, z_{l-1},
z_{l+1}, \dots, z_n) \), and we also define the function
\begin{equation}
  \Xi_l(z_l,\bm{z}_l) = \prod_{r<l}(z_l - z_r) \prod_{r>l}(z_r - z_l)\; , 
\end{equation}
then 
\begin{equation}
  \Delta(\bm{z}) = \Xi_l(z_l, \bm{z}_l) \Delta(\bm{z}_l) \; .
\end{equation}
\end{subequations}

Inserting this decomposition into~(\ref{eq:minor-expansion}), we find
\begin{equation}
\label{eq:minor-expansion-2}
  \bm{\tau}(\bm{z}, \bm{v})
   = \frac{1}{\Xi_l(z_l, \bm{z}_l)} \sum_{j=1}^n (-1)^{j + l} \frac{\mathcal{Y}_j(z_l)}{z_l - v_j} 
\left(\frac{1}{\Delta(\bm{z}_l)} \det[\hat{\Omega}_{j, l}]\right)\; .
\end{equation}

When we define the \(n\) sets of functions
\begin{equation}
  \begin{split}
    \hat{\bm{\Omega}}_{(j)}(z) & = \left(\Omega_1(z), \dots, \Omega_{j-1}(z), \Omega_{j+1}(z), \dots, \Omega_n(z) \right)\; ,
    \quad j =1, \dots, n\; ,
  \end{split}
\end{equation}
so that we can simplify the minor
expansion~(\ref{eq:minor-expansion-2}) even further; that is
\begin{equation}
\begin{split}
  \bm{\tau}(\bm{z}, \bm{v})
  & = \frac{1}{\Xi_l(z_l, \bm{z}_l)} \sum_{j=1}^n (-1)^{j + l} \frac{\mathcal{Y}_j(z_l)}{z_l - v_j} 
    \left(\frac{1}{\Delta(\bm{z}_l)} \det[\hat{\bm{\Omega}}_{(j) r}(\bm{z}_{(l) s} ]_{r, s=1}^n\right)\\ 
  & = \frac{1}{\Xi_l(z_l, \bm{z}_l)} \sum_{j=1}^n (-1)^{j + l} \frac{\mathcal{Y}_j(z_l)}{z_l - v_j} 
    \tilde{\bm{\tau}}_j(\bm{z}_l, \bm{v})\; ,
\end{split}
\end{equation}
where \(\hat{\bm{\Omega}}_{(j)r}\) is the \(r\)-th component of
\(\hat{\bm{\Omega}}_{(j)}\) and \(\hat{z}_{(l)s}\) is the \(s\)-th
component of \(\bm{z}_{(l)}\). Moreover, in the second line we have
defined the object
\begin{equation}
  \label{eq:basis-tau}
    \tilde{\bm{\tau}}_j(\bm{z}_l, \bm{v}) = 
\frac{1}{\Delta(\bm{z}_l)} \det[\hat{\bm{\Omega}}_{(j)}(\bm{z}_{(l)} ]\; .
\end{equation}
The curious aspect of this expression is that it easy to see that each term  
\(\tilde{\bm{\tau}}_j(\bm{z}_l, \bm{v})\) is a tau function itself, and that
it acts as a basis for the Slavnov's product. 
Additionally, these basis tau functions \(\tilde{\tau}_j(\bm{z}_l,
\bm{v})\) are, by construction, completely independent of \(z_l\).

@@

Therefore, we have the interesting result that the rresidues of the
tau function \(\tau(\bm{z}, \bm{v})\) for \(z_j\) approaching the
Bethe root \(v_j\) is proportional to a tau function.

\section{Homogeneous limit and Wronskian formula}

We the previous section we have discussed the limit where the
parameters \(\bm{z}\) approach the Bethe roots \(\bm{v}\).  We now
want to consider the limit where \(\bm{z}\) tend to a single variable,
say \(z_k\to z_1\), \(k=2,\dots, n\).
